Robust Bayesian Analysis of Causal Inference Problems

### 2022-10-27 JASA-template.tex
some more update

Bayesian approach in causal effect estimation has become a popular
topic in recent days. However, one of the earlier works on this can be
found in \cite{rubin1978}. Lately with the notion of variable selection
of high dimensional problems, Bayesian methodologies have become
more significant.

>>>>

Bayesian approach in causal effect estimation has become a popular
topic in recent days. However, one of the earlier works on this can be
found in \cite{rubin1978}. Lately with the notion of high dimensional problems, Bayesian methodologies have become
more appealing. \citet{Crainiceanu2008} proposed a bi-level 
Bayesian model averaging based method for estimating the causal 
effect. \citet{wang2015} suggested BAC (or, Bayesian adjustment for
confounding) where they use an informative prior obtained from
the treatment model and apply them on the outcome model for
estimating causal effect. Several other methods were also
proposed to tackle confounders from the point of view of Bayesian
variable selection such as: \citet{Zigler2014}, \citet{Hahn2018} etc.

In this paper we closely follow the approach of \citet{koch2020}, where
they proposed a bilevel spike and slab prior for causal effect 
estimation. They considered a data-driven adaptive approach to
reduce the variance of the causal estimate. Instead of that,
we suggest a robust Bayesian analysis based approach where instead
of using a single prior, we consider a set of priors \cite{BERGER1990303}. This is particularly interesting as in
many cases, causal effect estimation can be performed through a 
meta analysis and hence having a single prior can be problematic.
Moreover, for some problems we have to rely on very limited data to
perform our Bayesian analysis and choosing a data-driven prior
can lead to overfitting.
